### 2024-08-11 doc/Thesis/chapter/03-experimental.tex
start doing todo.md

\section{Substrate Preparation}
Five different substrates were used throughout this work: 
1 mm-thick, soda-lime microscope glass slides 
%\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5}) from Sigma Aldrich, thinner, 
squared glass plates (\cm{2.5}\x\cm{2.5}) Menzel Gläser,
\gls{ito} coated glass (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich with a sheet resistance of approximately 12 $\Omega$/sq, 
\gls{fto} coated glass (\cm{5}\x\cm{5}) from Sigma Aldrich and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
The steel foil was cut with a foil cutter into \cm{2.5}\x\cm{2.5} squares.
Glass was used because of its low price point and availability and to measure transmission and reflectance spectra. 
\Gls{fto} and \gls{ito} coated conducting substrates were used for \gls{sem} investigation and for electrical measurements (serving as one of the electrical contacts).
%\gls{fto} and \gls{ito} were used in order to have a conducting substrate. 
%, which is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
The conducting substrate allows for easy measurement of electric conductance in vertical direction.
Furthermore, while taking a \gls{sem} micrograph the sample would quickly accumulate negative charge and repel further electrons without a conducting substrate.
%The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
%The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in an ultrasonic bath
	\item \minutes{15} in \gls{water} in an ultrasonic bath
	\item \minutes{15} in \gls{ipo} in an ultrasonic bath 
\end{enumerate}
%\td{is that the usual procedure for steel?}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the coating step (cf. \cite{YAMASHITA2018,Kohli2010}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tape Casting}
\label{sec:exp-db}
All glass substrates were tape-casted manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied. %to create a valley in between. 
This allowed material to only be deposited on the area between the tape.
After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
%\td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

%Most steel substrates (all pre-optimization and optimization samples) 
%All 
Steel substrates were doctor bladed with an Erichsen Coatmaster 510 film applicator with a heatable plate.
%The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
%partially heated with a heat gun.
%The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in \SI{0.05}{\milli\meter} steps and \td{did not substantially alter the results. (what do you mean?)}
%For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
All experiments were performed with a blade height of \SI{0.2}{\milli\meter}.
%
%Eventually, a heatable vacuum plate was used. It 
The heatable vacuum plate had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where underpressure could be applied to keep the substrate in place. 
Most of them were covered with tape (see figure~\ref{fig:eric}) to increase the suction intensity at the remaining ones.
After setting the temperature of the heating plate to \SI{200}{\celsius}, the temperature of the vacuum plate 
(room temperature, \SI{40}{\celsius}, \SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) 
and the \gls{db} velocity (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimization, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the liquid evenly. 
After evaporation of the solution, the vacuum was turned off, the pushing bar
%'blade pusher' \td{film applicator, travel pusher, traverse something, pushing bar} 
was put into initial position, the blade was removed and excess solution was removed from the plate with a wipe. 
The coated substrate was dried for \minutes{5} on a \SI{200}{\celsius} heating plate.
%\td{transferred to the \SI{200}{\celsius} heating plate and rested on there for \minutes{5}. (why? what was the purpose?)}
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (\underline{1}) on the left,
		vacuum pump (\underline{2}) in the background and 
		Erichsen Coatmaster 510 film applicator (\underline{3}) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\milli\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

@@

%\todo{why didn't i just take this?}

@@

For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMIZATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pre-optimization of Coating Procedure}
\label{sec:exp-preopt}
%\td{preopt of what? recipe?}
%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
%\td{Screening}
%244 - 93 aqueous - 103 testing - 191 buthanol - 206 preopt - 244 emma
% 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
% 244 samples were produced: 93 samples with the aqueous recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).

%The first 200 recipes were optimized via biotic refinforcement learning (i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization. \td{(xxx but using a completely untested recipe!)} 
%The main part of all samples (200 out of 244) were pre-optimization samples,  from which the bulk were screening experiments optimized via biotic reinforcement learning  (i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization. \td{(xxx but using a completely untested recipe!)} 
%Initially, glass plates were doctor bladed manually with aqueous solution and calcinated 
%via HP1. 
%Glass was used because of its availability and in order to be able to make IR 
%\td{transmission} spectra.
%In order to measure the resistivity of the produced layer \gls{fto} and \gls{ito} layered 
%glass plates (both conductive) were used as substrate.
%Conducting substrates were also needed to produce \gls{sem} micrographs. 
%\td{should maybe put this into beginning of section \ref{sec:exp}?}
%otherwise the sample would charge and can't be pictured anymore. 
%this means if the produced layer is thick and homogeneous enough, it's difficult to see in sem
%Different additives were included in the recipe (see table \ref{tab:rec1}) and the resistance was checked with a multimeter. 
%\todo{different additives, heating programs (NT1-NT5 and HP1), blade distances (distance between blade and substrate) and layer counts were tried}
%Composition of the \td{aqueous solution (I thought this did not work?)}, heating program, blade distance (distance between blade and substrate) and layer count were varied but no homogeneous layers resulted. 
%
%The buthanolic recipe was introduced, which gave rise to homogeneous films.
%\td{After the blade moved over the substrate the remaining liquid needed about a minute to evaporate at room temperature. (2x mentioned this before!)}
%\td{
%The then current procedure resulted in clear and continuous films, but was plagued from inhomogeneities due to drying stains. 
%The drying stains could be circumvented by using a heat gun, but the results were not reproducible.

@@

%$T_{C}$[\oc{}]
%$v_{C}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a C machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see appendix~\ref{sec:app-pre-emma}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The stabilization agent was changed from \gls{acoh} to \gls{ipo} 
shortly before the \gls{pso}
because of much better solution stability and similar electric properties of resulting layers (see samples 192, 199 and 201 in appendix \ref{sec:app-pre-emma}).
The best process variables up to this point were chosen to be tested with 
\ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent showed comparable electric insulation results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
Therefore, \gls{ipo} was used  as stabilizer in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C velocity and C temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

\ds{The final boundaries were
conc 2 - 5 (1) ,
layers 4 - 12 (2),
\gls{db} velocity 10 - 20 (2),
\gls{db} temperature 20 - 80 (20),
heating rate 120 - 1080 (240),
calcination temp 300 - 500 (100),
.
}

>>>>

\section{Substrate Preparation}
Five different substrates were used throughout this work: 
1 mm-thick, soda-lime microscope glass slides 
%\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5}) from Sigma Aldrich, thinner, 
squared glass plates (\cm{2.5}\x\cm{2.5}) Menzel Gläser,
\gls{ito} coated glass (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich with a sheet resistance of approximately 12 $\Omega$/sq, 
\gls{fto} coated glass (\cm{5}\x\cm{5}) from Sigma Aldrich and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
The steel foil was cut with a foil cutter into \cm{2.5}\x\cm{2.5} squares.
Glass was used because of its low price point and availability and to measure transmission and reflectance spectra. 
\Gls{fto} and \gls{ito} coated conducting substrates were used for \gls{sem} investigation and for electrical measurements (serving as one of the electrical contacts).
%\gls{fto} and \gls{ito} were used in order to have a conducting substrate. 
%, which is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (dont follow?)}
The conducting substrate allows for easy measurement of electric conductance in vertical direction.
Furthermore, while taking a \gls{sem} micrograph the sample would quickly accumulate negative charge and repel further electrons without a conducting substrate.
%The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
%The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in an ultrasonic bath
	\item \minutes{15} in \gls{water} in an ultrasonic bath
	\item \minutes{15} in \gls{ipo} in an ultrasonic bath 
\end{enumerate}
%\td{is that the usual procedure for steel?}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the coating step (cf. \cite{YAMASHITA2018,Kohli2010}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tape Casting}
\label{sec:exp-db}
All glass substrates were tape-casted manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied. %to create a valley in between. 
This allowed material to only be deposited on the area between the tape.
After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
%\td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} speed was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

%Most steel substrates (all pre-optimization and optimization samples) 
%All 
Steel substrates were doctor bladed with an Erichsen Coatmaster 510 film applicator with a heatable plate.
%The rest was doctor bladed on a glass plate, initially fixed with double sided adhesive tape and 
%partially heated with a heat gun.
%The blade height was varied from \SI{0}{\milli\meter} to \SI{0.35}{\milli\meter} in \SI{0.05}{\milli\meter} steps and \td{did not substantially alter the results. (what do you mean?)}
%For the rest of the experiments a blade height of \SI{0.2}{\milli\meter} was used.
All experiments were performed with a blade height of \SI{0.2}{\milli\meter}.
%
%Eventually, a heatable vacuum plate was used. It 
The heatable vacuum plate had equally spaced circular \SI{2.5}{\milli\meter} diameter patches of porous metal where underpressure could be applied to keep the substrate in place. 
Most of them were covered with tape (see figure~\ref{fig:eric}) to increase the suction intensity at the remaining ones.
After setting the temperature of the heating plate to \SI{200}{\celsius}, the temperature of the vacuum plate 
(room temperature, \SI{40}{\celsius}, \SI{50}{\celsius}, \SI{60}{\celsius}, \SI{70}{\celsius} or \SI{80}{\celsius}) 
and the \gls{db} speed (\mmps{10}, \mmps{12}, \mmps{14}, \mmps{16}, \mmps{18} or \mmps{20}), 
the blade was put into its initial position, the sample was placed on the vacuum plate and the vacuum 
was switched on. 
During pre-optimization, lower \gls{db} velocities (\mmps{0.1}, \mmps{0.5}, 
\mmps{1}, \mmps{2} and \mmps{5}) were tested. 
\ul{100} of solution were 
applied with a 10 - \ul{1000} pipette and the blade moved over the sample distributing the liquid evenly. 
After evaporation of the solution, the vacuum was turned off, the pushing bar
%'blade pusher' \td{film applicator, travel pusher, traverse something, pushing bar} 
was put into initial position, the blade was removed and excess solution was removed from the plate with a wipe. 
The coated substrate was dried for \minutes{5} on a \SI{200}{\celsius} heating plate.
%\td{transferred to the \SI{200}{\celsius} heating plate and rested on there for \minutes{5}. (why? what was the purpose?)}
This process of applying a \gls{zro} layer was repeated as many times as needed.
\begin{figure}
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsen1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=.99\textwidth]{Pics/erichsendb1.png}
		\caption{}
	\end{subfigure}
	\caption{
		(a)
		Temperature regulator (\underline{1}) on the left,
		vacuum pump (\underline{2}) in the background and 
		Erichsen Coatmaster 510 film applicator (\underline{3}) with heatable vacuum plate.
        (b) Close up of the \gls{db} blade in position with blade height adjusted to \SI{0.2}{\milli\meter}.
		The majority of the suction areas is sealed with tape to increase the underpressure at the remaining ones.
	}
	\label{fig:eric}
\end{figure}

@@

%\todo{why did not i just take this?}

@@

For every I-V curve (i.e.\ for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMIZATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pre-optimization of Coating Procedure}
\label{sec:exp-preopt}
%\td{preopt of what? recipe?}
%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e.\ my brain)}
%\td{Screening}
%244 - 93 aqueous - 103 testing - 191 buthanol - 206 preopt - 244 emma
% 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
% 244 samples were produced: 93 samples with the aqueous recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).

%The first 200 recipes were optimized via biotic refinforcement learning (i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization. \td{(xxx but using a completely untested recipe!)} 
%The main part of all samples (200 out of 244) were pre-optimization samples,  from which the bulk were screening experiments optimized via biotic reinforcement learning  (i.e.\ my brain) in order to obtain reasonable constraints for computerized pre-optimization. \td{(xxx but using a completely untested recipe!)} 
%Initially, glass plates were doctor bladed manually with aqueous solution and calcinated 
%via HP1. 
%Glass was used because of its availability and in order to be able to make IR 
%\td{transmission} spectra.
%In order to measure the resistivity of the produced layer \gls{fto} and \gls{ito} layered 
%glass plates (both conductive) were used as substrate.
%Conducting substrates were also needed to produce \gls{sem} micrographs. 
%\td{should maybe put this into beginning of section \ref{sec:exp}?}
%otherwise the sample would charge and can not be pictured anymore. 
%this means if the produced layer is thick and homogeneous enough, it is difficult to see in sem
%Different additives were included in the recipe (see table \ref{tab:rec1}) and the resistance was checked with a multimeter. 
%\todo{different additives, heating programs (NT1-NT5 and HP1), blade distances (distance between blade and substrate) and layer counts were tried}
%Composition of the \td{aqueous solution (I thought this did not work?)}, heating program, blade distance (distance between blade and substrate) and layer count were varied but no homogeneous layers resulted. 
%
%The buthanolic recipe was introduced, which gave rise to homogeneous films.
%\td{After the blade moved over the substrate the remaining liquid needed about a minute to evaporate at room temperature. (2x mentioned this before!)}
%\td{
%The then current procedure resulted in clear and continuous films, but was plagued from inhomogeneities due to drying stains. 
%The drying stains could be circumvented by using a heat gun, but the results were not reproducible.

@@

%$T_{C}$[\oc{}]
%$v_{C}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading speed.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a C machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see appendix~\ref{sec:app-pre-emma}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The stabilization agent was changed from \gls{acoh} to \gls{ipo} 
shortly before the \gls{pso}
because of much better solution stability and similar electric properties of resulting layers (see samples 192, 199 and 201 in appendix \ref{sec:app-pre-emma}).
The best process variables up to this point were chosen to be tested with 
\ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent showed comparable electric insulation results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
Therefore, \gls{ipo} was used  as stabilizer in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C speed and C temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} speed  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

\ds{The final boundaries were
conc 2 - 5 (1) ,
layers 4 - 12 (2),
\gls{db} speed 10 - 20 (2),
\gls{db} temperature 20 - 80 (20),
heating rate 120 - 1080 (240),
calcination temp 300 - 500 (100),
.
}

### 2024-08-11 doc/Thesis/chapter/04-computational-details.tex
start doing todo.md

\section{Evolutionary Model-based Multiresponse Approach (EMMA)}
\label{sec:ss}
%\todo{for what?}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$n_L$	&$T_{C}$[\oc{}]	&$v_{C}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $n_L$ and $v_{cal}$, 
(i.e. conducticity, pinhole density, number of coated layers and heating rate)
where $\gamma$, $\rho$ and $n_L$ are to be minimized and $v_{cal}$ to be maximized.
%which all should be minimized except for $v_{cal}$.
The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The samples are produced, the \gls{iv} curves are measured and the measurements evaluated according to section 
\ref{sec:exp}, yielding the quantities 
$\gamma$, $\rho_s$, $n_L$ and $v_{cal}$, which were used as inputs for the program.
% and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), $n_L$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program.

>>>>

\section{Evolutionary Model-based Multiresponse Approach (EMMA)}
\label{sec:ss}
%\todo{for what?}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e.\ experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$n_L$	&$T_{C}$[\oc{}]	&$v_{C}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $n_L$ and $v_{cal}$, 
(i.e.\ conductivity, pinhole density, number of coated layers and heating rate)
where $\gamma$, $\rho$ and $n_L$ are to be minimized and $v_{cal}$ to be maximized.
%which all should be minimized except for $v_{cal}$.
The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The samples are produced, the \gls{iv} curves are measured and the measurements evaluated according to section 
\ref{sec:exp}, yielding the quantities 
$\gamma$, $\rho_s$, $n_L$ and $v_{cal}$, which were used as inputs for the program.
% and the responses conductivity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), $n_L$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in \oc{}/\minutes{}) are supplied to the program.
